---
title: "molly10_finalHomeworkCode_01"
author: "Yinuo Mao"
date: "2025-02-07"
output: html_document
---

```{r}
library(tidyverse) # includes stringr)
```

##Challenge 1

```{r}
sentence <- "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."

# Remove punctuation
Ulysses_sentence <- gsub("[[:punct:]]", "", sentence)

# Split into a vector of words
words_vector <- unlist(str_split(Ulysses_sentence, "\\s+"))

# Extract every third word
third_words <- words_vector[seq(3, length(words_vector), by = 3)]

# Display the result
third_words
```
```

##Challenge 2

```{r}
# Given a matrix m
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)

# Select 2nd, 3rd, and 6th columns
a <- m[,c(2, 3, 6)]

# Print
print(a)

# Select 6th to 8th rows
b <- m[6:8, ]

# Print b
print(b)

# Select elements from row 2, column 2 to row 6, column 9
c <- m[2:6, 2:9]

# Print c
print(c)
```

##Challenge 3

```{r}
# Create a 4-dimensional, 400-element array
a <- array(400:1, dim = c(5, 5, 4, 4))

# Display the outcomes
a[1, 1, 1, 2]

a[2, 3, 2, ]

a[1:5, 1:5, 3, 3]

# Print
print(a)
```

##Challenge 4

```{r}
## Lemuroidea
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")

## Lorisoidea
Lorisoidea <- c("Lorisidae", "Galagidae")

#### The Strepsirhini group (Lemuroidea and Lorisoidea)
Strepsirhini <- list(Lemuroidea = Lemuroidea, Lorisoidea = Lorisoidea)

## Tarsioidea
Tarsioidea <- c("Tarsiidae")

# The Catarrhini group (Hylobatidae, Hominidae, and Cercopithecidae)
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")

# The Platyrrhini group
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")

## The Anthropoidea group
Anthropoidea <- list(Platyrrhini = Platyrrhini, Catarrhini = Catarrhini)

### The Haplorhini group
Haplorhini <- list(Anthropoidea = Anthropoidea, Tarsioidea = Tarsioidea)

#### Combine Haplorhini and Strepsirhini into the Primates group
Primates <- list(Haplorhini = Haplorhini, Strepsirhini = Strepsirhini)

# Print the list
Primates
```

##Challenge 5

```{r}
# make a matrix, stored by rows
m3 <- matrix(c(3, 0, 1, 23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)

# Coerce the matrix to a data frame
df <- as.data.frame(m3)

# Coerce the second column to be logical-valued
df[[2]] <- as.logical(df[[2]])

# Coerce the third column to be factor-valued
df[[3]] <- as.factor(df[[3]])

# Display the structure of the dataframe
str(df)
```

